Internet of Things code deployment metrics

### 2014-11-09 opdracht_2/beamer.tex
design

\begin{frame}[label=sec-1-6]{Belangrijke aspecten bij WSN design}
\begin{itemize}
\item energie-efficiëntie
\item robuustheid
\item autonomie
\end{itemize}
\end{frame}

>>>>

\begin{frame}[label=sec-1-6]{Belangrijke aspecten bij WSN design}
\begin{center}

\vfill
\begin{tabular}{l c r}
\hiddencell{1}{\includegraphics[width=0.25\textwidth,keepaspectration=true]{wsndesign/battery.png}} & \hiddencell{2}{\includegraphics[width=0.25\textwidth,keepaspectration=true]{wsndesign/density.png}} & \hiddencell{3}{\includegraphics[width=0.15\textwidth,keepaspectration=true]{wsndesign/euro.png}}  \\
\hiddencell{1}{Energieverbruik} & \hiddencell{2}{Dichtheid} & \hiddencell{3}{Goedkoop}\\
%
\hiddencell{4}{} & \hiddencell{5}{}\\
\hiddencell{4}{} & \hiddencell{5}{}\\
\hiddencell{4}{Autonoom} & \hiddencell{5}{Adaptief}
\end{tabular}
\vfill

\end{center}
\note{Consume extremely low power, operate in high volumetric densities, have low production cost and be dispensable, be autonomous and operate unattended, be adaptive to the environment.}
\end{frame}
